---
title: "Free Recall Example"
author: "Nicholas Maxwell, Erin Buchanan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Free Recall Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Libraries and Data 

Please see manuscript for a long description of the following data. We will load the example data, and you can use the `?` with the dataset name to learn more about the data.  

```{r}
library(lrd)
data("wide_data")
head(wide_data)
#?wide_data

data("answer_key_free")
head(answer_key_free)
#?answer_key_free

library(ggplot2)
```

# Data Restructuring

```{r}
DF_long <- arrange_data(data = wide_data,
      responses = "Response",
      sep = ",",
      id = "Sub.ID")
head(DF_long)
```

# Data Cleanup

Scoring in `lrd` is case sensitive, so we will use `tolower()` to lower case all correct answers and participant answers. 

```{r}
wide_data$Response <- tolower(wide_data$Response)
answer_key_free$Answer_Key <- tolower(answer_key_free$Answer_Key)
```

# Score the Data

You should define the following:

- data = dataframe of participant responses
- responses = column name of the participant answers
- key = column name of the answer key
- id = column name of the participant id number
- cutoff = the Levenshtein distance value you want to use for scoring (0 no changes exactly the same, higher numbers allow more variance in the word)
- flag = calculate z scores for outliers (TRUE/FALSE)
- group.by = column name(s) for grouping variables

```{r}
free_output <- prop_correct_free(data = DF_long,
                                 responses = "response",
                                 key = answer_key_free$Answer_Key,
                                 id = "Sub.ID",
                                 cutoff = 1,
                                 flag = TRUE,
                                 group.by = "Disease.Condition")


str(free_output)
```

# Output

We can use `DF_Scored` to see the original dataframe with our new scored column - also to check if our answer key and participant answers matched up correctly! The `DF_Participant` can be used to view a participant level summary of the data. Last, if a grouping variable is used, we can use `DF_Group` to see that output. 

```{r}
#Overall
free_output$DF_Scored

#Participant
free_output$DF_Participant

#Group
free_output$DF_Group
```

# Other Possible Calculations

## Serial Position

```{r}
serial_output <- serial_position(data = free_output$DF_Scored,
                                 key = answer_key_free$Answer_Key,
                                 position = "position",
                                 scored = "Scored",
                                 answer = "Answer",
                                 group.by = "Disease.Condition")

head(serial_output)

ggplot(serial_output, aes(Tested.Position, Proportion.Correct, color = Disease.Condition)) +
  geom_line() +
  geom_point() +
  xlab("Tested Position") +
  ylab("Probability of First Response") +
  theme_bw() 
```

## Conditional Response Probability

```{r}
crp_output <- crp(data = free_output$DF_Scored,
                  key = answer_key_free$Answer_Key,
                  position = "position",
                  scored = "Scored",
                  answer = "Answer",
                  id = "Sub.ID")

head(crp_output)

crp_output$participant_lags <- as.numeric(as.character(crp_output$participant_lags))

ggplot(crp_output, aes(participant_lags, CRP, color = Disease.Condition)) +
  geom_line() +
  geom_point() +
  xlab("Lag Distance") +
  ylab("Conditional Response Probability") +
  theme_bw()
```

## Probability of First Response

```{r}
pfr_output <- pfr(data = free_output$DF_Scored,
                  key = answer_key_free$Answer_Key,
                  position = "position",
                  scored = "Scored",
                  answer = "Answer",
                  id = "Sub.ID",
                  group.by = "Disease.Condition")

head(pfr_output)

pfr_output$Tested.Position <- as.numeric(as.character(pfr_output$Tested.Position))

ggplot(pfr_output, aes(Tested.Position, pfr, color = Disease.Condition)) +
  geom_line() +
  geom_point() +
  xlab("Tested Position") +
  ylab("Probability of First Response") +
  theme_bw()
```



